### 2015-11-19 section/0_intro.tex
addressing issues in first 3 sections based on yesterday's discussion

Figure~\ref{fig:GCC27733} shows a real-world performance bug in GCC. 
Function \texttt{mult\_alg} is used to compute the best algorithm for 
multiplying \texttt{t}. It is so time consuming that developers used a
hash-table
\texttt{alg\_hash} to remember which \texttt{t} has been processed
in the past and what is the result. 
Unfortunately, a mistake in the type declaration of hash-table
entry \texttt{hash\_entry} makes the memoization useless for large \texttt{t},
severely hurting performance.
In reality, developers easily figured out that function
\texttt{mult\_alg} is most correlated with the execution slowness, but
spent several weeks to finally figure out \texttt{mult\_alg} is in fact
inefficient.
%If a tool can tell them not only which loop\footnote{Recursive functions are
%handled similarly as loops in this paper.}
%is the root cause but also why a loop is inefficient (i.e., lot of redundant
%computation and the need for better memoization in this example), 
%the diagnosis and bug fixing
%process would be much easier for developers.

>>>>

Figure~\ref{fig:GCC27733} shows a performance bug in GCC. 
Function \texttt{mult\_alg} is used to compute the best algorithm for 
multiplying \texttt{t}. It is so time consuming that developers used a
hash-table
\texttt{alg\_hash} to remember which \texttt{t} has been processed
in the past and what is the result. 
Unfortunately, a mistake in the type declaration of hash-table
entry \texttt{hash\_entry} makes the memoization useless for large \texttt{t},
severely hurting performance.
In reality, developers easily figured out that
\texttt{mult\_alg} is most correlated with the execution slowness, but
spent several weeks to finally figure out \texttt{mult\_alg}, 
containing 400 lines
of code, is
inefficient.
%If a tool can tell them not only which loop\footnote{Recursive functions are
%handled similarly as loops in this paper.}
%is the root cause but also why a loop is inefficient (i.e., lot of redundant
%computation and the need for better memoization in this example), 
%the diagnosis and bug fixing
%process would be much easier for developers.

### 2015-11-19 section/2_workless.tex
addressing issues in first 3 sections based on yesterday's discussion

\item Static-dynamic hybrid analysis. As we will see, static analysis alone
will not be able to provide all the needed information to judge whether
a loop is problematic. However, 
dynamic analysis alone will incur too much overhead.
Therefore, we use a hybrid approach throughout our design.

@@

\Tool first identifies side-effect instructions that write to
variables defined outside the loop. 
\Tool analyzes all functions that are called
by a loop directly or indirectly --- a function $F$ that updates variables
defined outside $F$ makes the corresponding call statement in $F$'s
caller a side-effect instruction.
We consider all library functions or function calls through function pointers 
as functions that have side effects, 
unless the library functions are specially marked by us in a white list.

\Tool then categorizes loops into four types.
Loop 0* contains no side-effect instructions. 
Loop 1* contains at least one side-effect instruction along every path that
starts from the loop header and ends at the loop header.
For the remaining cases, 
when the basic block with side-effect instructions
is part of the natural loop, the case
belongs to [0$|$1]*; instead, if the side-effect basic block is post-dominated
by one of the loop-exit blocks and is dominated by the loop header, yet is
not part of the natural loop, the case belongs to 0*1?.

>>>>

\item Static-dynamic hybrid analysis. Static analysis alone
will not be able to provide all the needed information to judge whether
a loop is inefficient. However, 
dynamic analysis alone will incur too much overhead.
Therefore, we use a hybrid approach throughout our design.

@@

\Tool first identifies side-effect instructions that write to
variables defined outside the loop. 
\Tool analyzes all functions called
by a loop directly or indirectly --- a function $F$ that updates variables
defined outside $F$ makes the corresponding call statement in $F$'s
caller a side-effect instruction.
We consider all calls to library functions or through function pointers 
as having side effects, 
unless the library functions are specially marked by us in a white list.

\Tool then categorizes loops into four types.
Given a natural loop $l$, when $l$
contains at least one side-effect instruction along every path that
starts from the loop header and ends at the loop header, it is a 1* loop;
if there exists at least one side-effect instruction inside $l$, but not on
every path,
it is a [0$|$1]* loop; if there is no side-effect instructions inside $l$,
$l$ is either a 0* or a 0*1? loop.
In the last case, \Tool further checks all the loop exit-blocks. If there 
exists an exit-block of $l$ that contains a side-effect instruction and is  
post-dominated by another exit-block of $l$, this is a 0*1? loop.
For example, line 5 in Figure \ref{fig:Mozilla347306} is such an exit block.
Otherwise, $l$ is a 0* loop.
